Intentional release of native species undermines ecological stability

### 2022-10-21 rmd/supporting_info.Rmd
rmd
Update supporting_info.Rmd

**Fish release.** The release of masu salmon began in the 1950s. Hatchery fish are reared in captivity for zero (wild origin) to seven generations (the majority is two to four generations). Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Most fish are released near the fish survey sites. However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable. For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

@@

knitr::kable(df_prior,
             format = "markdown",
             caption = "Prior distributions used in the Bayesian models. See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors. The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).")

@@

# References

>>>>

**Fish release.** The release of masu salmon began in the 1950s. The duration of captivity ranged from zero (wild origin) to seven generations, and the majority is released at two to four generations in captivity. Although the program aims to release a constant number of hatchery fish for each watershed, uncontrollable factors (e.g., disease, budget allocation) produce some variation in the number of releases among years. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Most fish are released near the fish survey sites. However, the number of fish released at each site was reported as an aggregate for each watershed, and the site-specific information of release is unavailable. For each release stage, we assembled annual records of intentional release (the number of fish released; 1999 -- 2019) from annual investigations by the Japan Fisheries Research and Education Agency and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of release took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

@@

knitr::kable(df_prior,
             align = rep("l", 3),
             format = "markdown",
             caption = "Prior distributions used in the Bayesian models. See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors. The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).")

@@

```{=tex}
\fancyhead[L]{Terui et al.}
\fancyhead[C]{}
\fancyhead[R]{}
```
# References
